Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
results description

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.45\textwidth]{pictures/metodyka_badan.png}
\caption{Methods of testing carried out to test of the variable size window}
\label{research_methods}
\end{center}
\end{figure}
\FloatBarrier

Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} show the cumulative profit for the test period equal to 100 for the two treatment strategies.

@@

\caption{Chart of the cumulative profit for the strategy for test period equal 100}
\end{figure}
\FloatBarrier

It may be noted that the two policies, the test period of 100, the products allow for systematic performance gain over the period with
 only small landslides. Profit for the final strategy is TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094. 
Smaller decreases are for the second strategy. In addition, it confirms the higher the Calmar ratio - 12.79, 
when the first of these strategies is on 10.22.
According to the authors, these are excellent, achieved on sections of the test, not the learning episodes.
 The latter, of course, achieved significantly better results matching classifier. It is also understood asymmetry results for the two strategies
 - the first one is focused on horizontal trend, the other on a downward trend. The results depend on the nature of the market, 
which is considered by learning strategies automatically. Perhaps at another time, for other data these results could be different.
In addition to the basic performance of the length of the test period equal to 100, a number of studies conducted on different lengths
 of the period. There may be more favorable long test window than arbitrarily selected window above the 100 candles.\\

Below, we present four graphs showing the results of the strategy TewiMiC. The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the gain curve in time.
To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
 From Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
 The window 100 reflects quite well so desired test section.
\begin{figure}[h!]
\begin{minipage}{.45\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{pictures/cumulativeReturnsC.png}
\subcaption{Results in 3D}
\label{Cum3DMiC}
\end{center}
\end{minipage}
\begin{minipage}{.45\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{pictures/mic_end.png}
\subcaption{Final results}
\label{Cum3DMiCend}
\end{center}
\end{minipage}
\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.45\textwidth]{pictures/metodyka_badan.png}
\caption{Methods of testing carried out to test the variable size window}
\label{research_methods}
\end{center}
\end{figure}
\FloatBarrier

Figures ~\ref{MiC100} and ~\ref{MiD100} on page ~\pageref{MiD100} shows the cumulative profit for the test period equal to 100 candles (hours) for the two examined strategies.

@@

\caption{Chart of the profit for the strategy with fixed test period size - 100 candles}
\end{figure}
\FloatBarrier

It may be noted that the two policies, for the test period of 100, allow for systematic profit in examined period with only for small drawndowns. Profit for the strategy TewiMiC 0.355, for TewiMiD profit is several times smaller and amounts to 0.094. But second strategy has smaller drawndowns. In addition, it is confirmed with the higher Calmar ratio - 12.79, where the result for first of these strategies is 10.22. According to the authors, results are excellent, achieved on testing sections, not on the learning periods. On learning periods, of course, significantly better results were achieved with classifier matching. It is also clear that asymmetry results for the two strategies arise from different approaches - the first one is focused on horizontal trend, the other on a downward trend. The results depend on the nature of the market, which is automatically founded by learning strategies. Perhaps at another period of time, for other data these results could be different. In addition to the basic performance of the length of the test period equal to 100, a number of studies were conducted on different lengths of the testing period. There may be more favorable length of test window than arbitrarily selected window length of 100 candles.\\

Below, we present four graphs showing the results of the strategy TewiMiC. The first of these (Figure \ref{Cum3DMiC} on page \pageref{Cum3DMiC}) shows the effect of test duration on the profit curve in time. To see more detail for how long the test period are achieved optimal results plotted showing 2D final profit for each of the three sizes.
 From Figure \ref{Cum3DMiCend} on page \pageref{Cum3DMiCend} shows that the number of candles for achieving a high and satisfactory results are attributable to 80-120.
 The window 100 reflects quite well so desired test section.
\begin{figure}[h!]
\begin{minipage}{.45\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{pictures/cumulativeReturnsC.png}
\subcaption{Results in 3D}
\label{Cum3DMiC}
\end{center}
\end{minipage}
\begin{minipage}{.45\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{pictures/mic_end.png}
\subcaption{Final results}
\label{Cum3DMiCend}
\end{center}
\end{minipage}
\caption{Earnings accumulated over time, depending on the length of the test period for TewiMIC}
\end{figure}
\FloatBarrier
